\songtitle{Willie Moore}{\narrative\\\death}

% Lyrics need to be checked

\versemark
Willie Moore was a king, his age twenty-one,\\*
He courted a damsel fair;\\
Oh, her eyes was as bright as the diamonds every night,\\*
And wavy black was her hair.

\versemark
He courted her both night and day,\\*
Till to marry they did agree;\\
But when he came to get her parents consent,\\*
They said it could never be.

\versemark
She threw herself in Willie Moore’s arms,\\*
As ofttime had done before;\\
But little did he think when they parted that night,\\*
Sweet Anna he would see no more.

\versemark
It was about the tenth of May,\\*
The time I remember well;\\
That very same night, her body disappeared\\*
In a way no tongue could tell.

\versemark
Sweet Annie was loved both far and near,\\*
Had friends most all around;\\
And in a little brook before the cottage door,\\*
The body of sweet Anna was found.

\versemark
She was taken by her weeping friends,\\*
And carried to her parent’s room,\\
And there she was dressed in a gown of snowy white,\\*
And laid her in a lonely tomb.

\versemark
Her parents now are left all alone,\\*
One mourns while the other one weeps;\\
And in a grassy mound before the cottage door,\\*
The body of sweet Anna still sleeps.

\versemark
Willie Moore never spoke that anyone heard,\\*
And at length from his friends did part,\\
And the last heard from him, he’d gone to Montreal,\\*
Where he died of a broken heart.

\versemark
This song was composed in the flowery West\\*
By a man you may never have seen;\\
Oh, I’ll tell you his name, but it is not in full,\\*
His initials are J.R.D.

% https://www.youtube.com/watch?v=DLwK-nT4btU

\attribution{Allison de Groot and Tatiana Hargreaves, performers}
