\songtitle{Deliverance will come}{\religious}
\qv{Palms of victory}

\notes{f \major}{2/4}{\partial 8 a16( g) f8. f16 f8 f f f4 f8 g8. g16 g8 g a4.}\contd
\notescontd{f \major}{2/4}{\repeat volta 2 {\partial 8 g8 a c c8. d16 c8 a4 f8 g8. f16 f8 f f4.}}

\versemark
I saw a wayworn traveler,\\*
In tattered garments clad,\\
And struggling up the mountain,\\*
It seemed that he was sad;

His back was laden heavy,\\*
His strength was almost gone,\\
Yet he shouted as he journeyed,\\*
Deliverance will come!

\notescontd{f \major}{2/4}{\partial 8 \repeat volta 2 {\bar ".|:" a16( g) f4. f8 f8. f16 f8( a) g4. g8 a( c) c4 c4. d8 c8. a16 f4 g8( f) a( g) f4.}}

\chorus{Then palms of victory,\\*
Crowns of glory,\\*
Palms of victory\\*
I shall wear.}

\versemark
The summer sun was shining,\\*
The sweat was on his brow,\\
His garments worn and dusty,\\*
His step seemed very slow;

But he kept pressing onward,\\*
For he was wending home,\\
Still shouting as he journeyed,\\*
Deliverance will come!

[The songsters in the arbor\\*
That stood beside the way\\
Attracted his attention,\\*
Inviting his delay:

His watchword being Onward!\\*
He stopped his ears and ran,\\
Still shouting as he journeyed,\\*
Deliverance will come!]

\versemark
I saw him in the evening;\\*
The sun was bending low;\\
He’d overtopped the mountain,\\*
And reached the vale below:

He saw the Golden City—\\*
His everlasting home—\\
And shouted loud, Hosanna!\\*
Deliverance will come!

[While gazing on that city,\\*
Just o’er the narrow flood,\\
A band of holy angels\\*
Came from the throne of God;

They bore him on their pinions\\*
Safe o’er the dashing foam,\\
And joined him in his triumph:\\*
Deliverance had come!]

\versemark
I heard the song of triumph\\*
They sang upon that shore,\\
Saying, Jesus has redeemed us\\*
To suffer nevermore!

Then casting his eyes backward\\*
On the race which he had run,\\
He shouted loud, Hosanna!\\*
Deliverance has come!

\attribution{Roud 3540; John B. Matthias, lyricist, composer}
