\songtitle{Drive dull care away}{\company}

\notes{b \minor}{4/4}{\repeat volta 2 {\partial 4 b4 fis fis fis e8( d) e4 e fis8( gis) a4 fis d e8( d) cis4 b2 r4}}

\versemark
Oh why should we our lot complain,\\*
Or grieve at our distress?\\
Some think if they could riches gain,\\*
’Twould be true happiness.

\notescontd{b \minor}{4/4}{\partial 4 fis4 b4. cis8 d4 cis8( b) a8 b4. fis2 b4. cis8 d4 b b8*2/3[ a fis] b4(^\markup{\hspace#0.5 \musicglyph #"scripts.turn"} a4*2\fermata) \bar "||"}\contd
\notescontd{b \minor}{4/4}{\repeat volta 2 {\partial 4 a a b fis e8 d e4 e fis8( gis) a4 fis d e8( d) cis4 b2 r4}}

But alas, how vain is all their strife,\\*
Life’s cares it will not allay;\\
\chorusfont{So while we’re here with our friends so dear,}\\*
\chorusfont{We’ll drive dull care away.}

\chorus{Away, away, away, away,\\*
We will drive dull care away;\\
So while we’re here with our friends so dear,\\*
We’ll drive dull care away.}

\versemark
Why should the rich despise the poor?\\*
Why should the poor repine?\\
When we will all in a few short years,\\*
In equal friendship join.

They’re both to blame, they’re all the same,\\*
We are all made of one clay;\\
\chorusfont{So while we’re here with our friends so dear,}\\*
\chorusfont{We’ll drive dull care away.}\refrain

\versemark
The only circumstance in life,\\*
Which I could ever find;\\
To conquer care or temper strife,\\*
Was a contented mind.

With this in store we have much more,\\*
Than all things else can convey;\\
\chorusfont{So while we’re here with our friends so dear,}\\*
\chorusfont{We’ll drive dull care away.}\refrain

\versemark
So let us make the best of life,\\*
Not rendering it a curse;\\
But take it as you would a wife,\\*
For better or for worse.

Life at its best is but a jest,\\*
Like a dreary winter’s day;\\
\chorusfont{So while we’re here with our friends so dear,}\\*
\chorusfont{We’ll drive dull care away.}\refrain

\attribution{Roud 13988; John Roberts, Debra Cowan, performers}
