\songtitle{Pleasant and delightful}{\love}
\qv{Larks they sang melodious}

\notes{g \major}{6/4}{\partial 4 b,8. c16 d4 b' a8. fis16 g4 d b8. c16 d4 g fis g2 \repeat volta 2 { g8. a16 b4 g c8. b16 b4 a} \bar ""}\contd
\notescontd{g \major}{6/4}{\repeat volta 2 {\partial 4 b8. a16 g4 fis e d2 } b'8. c16 d4.-- c8 b[ a] g[ e] c'4\fermata \bar "'" d8. c16 b8. a16 g4 fis g2 \bar "||"}

\versemark
It was pleasant and delightful on a midsummer’s morn,\\*
\mbox{And the green fields and the meadows were all covered in corn,}\\
And the blackbirds and thrushes sang on every green spray,\\*
And the larks they sang melodious\\*
\vin at the dawning of the day.

\notescontd{g \major}{6/4}{\partial 4 g8. fis16 e4 c a'8. g16 fis8. e16 d4\fermata \bar "'" g8. a16 b4.-- g8 c[ b] b8. a16 a4\fermata \bar "'"}\contd
\notescontd{g \major}{6/4}{\partial 4 b8. c16 d4.-- c8 b[ a] g[ e] c'4\fermata \bar "'" d8. c16 b8. a16 g4 fis g2 \bar "||"}

\chorusfont{And the larks they sang melodious,\\*
And the larks they sang melodious,\\*
And the larks they sang melodious,\\*
\vin at the dawning of the day}

\versemark
Now a sailor and his true love were a-walking one day\\*
Said the sailor to his true love, I am bound far away\\
I am bound for the East Indies where the loud cannons roar\\*
And I’m bound to leave you, Nancy –\\*
\vin you’re the girl that I adore\simile

\versemark
Then the ring from off her finger she instantly drew\\*
Saying, Take this, dearest William, and my heart will go too.\\
And as they were embracing tears from her eyes fell,\\*
Saying, May I go along with you?\\*
\vin — Oh no, my love, farewell!\simile

\versemark
Fare thee well my dearest Nancy, no longer can I stay\\*
For the topsails are hoisted and the anchors aweigh\\
And the ship she lies waiting for the fast flowing tide\\*
And if ever I return again,\\*
\vin I will make you my bride\simile

\attribution{Roud 660}
