\songtitle{Rolling down to Old Maui}{\sea\\\sturdy}

\notes{c \minor}{4/4}{\partial 4 c4 f f e c8 c as'4 as g \bar "'" c8( bes) as( g) f4 g8( f) es4 f2. \bar "'"}\contd
\notescontd{c \minor}{4/4}{\partial 4 c4 f f e c8 c as'4 g8( f) g4 \bar "'" c8( bes) as( g) f4 g8( f) es4 f2. \bar "'"}

\versemark
It’s a damn tough life full of toil and strife\\*
We whalermen undergo\\
And we don’t give a damn when the day is done\\*
How hard the winds do blow.

\notescontd{c \minor}{4/4}{\partial 4 as8( bes) c4 c c bes8 as bes4 bes bes \bar "'" as8 g as4 bes as8( g) f4 g2. \bar "'"}\contd
\notescontd{c \minor}{4/4}{\partial 4 f8 f f4 g8( f) e4 c8 c as'4 as g \bar "'" c8 bes as4. f8 g( f) es4 f2. \bar "||" }

We’re homeward bound from the Arctic ground\\*
With a good ship, taut and free\\
And we won’t give a damn when we drink our rum\\*
With the girls of Old Maui.

\notes{c \minor}{4/4}{\partial 2 as4 bes c4. c8 c( bes) as4 bes4. bes8 bes4 \bar "'" as8 g as4. as8 as( g) f4 g2. \bar "'"}\contd
\notes{c \minor}{4/4}{\partial 4 c4 f f e c8 c as'4 as g \bar "'" c8 bes as4. f8 g( f) es4 f2. \bar "||"}

\chorus{Rolling down to Old Maui, me boys\\*
Rolling down to Old Maui\\
We’re homeward bound from the Arctic ground\\*
Rolling down to Old Maui.}

\versemark
Once more we sail with a northerly gale\\*
Through the ice and wind and rain.\\
Them coconut fronds, them tropical lands\\*
We soon shall see again.

Six hellish months have passed away\\*
On the cold Kamchatka Sea,\\
But now we’re bound from the Arctic ground\\*
Rolling down to Old Maui \refrain

\versemark
And now we sail with a favourable gale\\*
Towards our island home.\\
Our mainmast sprung, our whaling done\\*
And we ain’t got far to roam

Our studsail bones got carried away\\*
What care we for that sound?\\
A living gale is after us\\*
Thank God we’re homeward bound. \refrain

\attribution{Roud 2005; The Revels (group), performer}
